Model LF

### 2022-10-20 max_dp endogen stød.Rmd
Commit

COMMENT> 
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_low <= 0 & sens2_up <= 0
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_up > 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2_low > 0

>>>>

COMMENT> 
IDENTITY> max_gap
EQ> max_gap = 0.40
IF> sens2_low <= 0 & sens2_up <= 0
IDENTITY> max_gap
EQ> max_gap = 0.42
IF> sens2_up > 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2_low > 0
